---
title: "A fuller simulation"
author: "Lyndon Estes"
date: "October 27, 2015"
output: 
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes 
---

# Overview

Having examined the manner in which different weightings alter the impacts of different land use priorities, you can now choose a few of those weighting schemes and explore them more fully in relation to different crop production targets.  

# Set parameters

Give a reasoned value for the future target for each of the 9 crops in the `prod_targ` vector below. The values you give are a multiplier relative to current levels of production. Below that, give the values of the weights you want to apply to each of the four land use priorities, in the `cbeta` vector. 
```{r}
# production target list
prod_targ <- c("maize" = 4, 
               "cassava" = 2, 
               "ground" = 2, 
               "cotton" = 2, 
               "soy" = 2, 
               "pulse" = 2, 
               "sunflower" = 2, 
               "sugarcane" = 2, 
               "wheat" = 2)

# cbeta vector
cbetas <- c("Ag" = 0.5, 
            "C" = 0.5, 
            "bd" = 0, 
            "cost" = 0)

```

# Run the model
```{r, echo = FALSE, eval = FALSE}
library(agroEcoTradeoff)
bcode <- run_code("ZA")
dnm <- paste0(full_path(set_base_path(), "external/output/batch/dt/"), bcode)
dir.create(dnm)

# Run model
ybetas <- list(1, 1)
tdt <- tradeoff_mod(prod_targ, ybetas, cbetas)  # 2.5 seconds

# Write out outputs
fnm <- full_path(set_base_path(), 
                 paste0("external/output/batch/dt/", bcode, "/", 
                        tdt$runcode, ".csv"))
write.table(tdt$conv, file = fnm, sep = ",", col.names = TRUE, 
            row.names = FALSE)
impacts <- tdt[[c("impacts")]]

fnm <- full_path(set_base_path(), 
                 paste0("external/output/batch/dt/", bcode, "/impacts.rda"))
save(impacts, file = fnm)
save(bcode, file = paste0("external/output/batch/dt/bcode.rda"))
```

# Plot results

## Where were the impacts?
```{r, echo = FALSE, message=FALSE}
library(agroEcoTradeoff)
setwd(set_base_path())
load(paste0("external/output/batch/dt/bcode.rda"))
CRSobj <- spatial_meta("ZA")$crs
dnm <- full_path("external/output/batch/dt", bcode)
dt <- fread(full_path(dnm, dir(dnm, pattern = ".csv")))

xy <- dt[, .(x, y)]
xy[, conv := dt[, rowSums(.SD), .SDcols = names(dt)[-c(1:2)]]]
dtr <- dt_to_raster(xy, CRSobj = CRSobj)

load(paste0(dnm, "/impacts.rda"))

v1 <- sum(impacts$conv_area) / 1000
v2 <- sum(impacts$pa_loss) / 1000
v3 <- mean(impacts[, 3], na.rm = TRUE)
v4 <- mean(impacts[, 5], na.rm = TRUE)

par(mar = c(1, 1, 1, 1))
plot(dtr, axes = FALSE, box = FALSE, legend = FALSE)
mtext(paste(v1, "ha converted"), side = 3, adj = 0)
mtext(paste(v2, "PA ha converted"), side = 3, adj = 0, line = -1)
mtext(paste(round(v3, 1), "spp/tYield"), side = 3, adj = 0, line = -2)
mtext(paste(round(v4, 1), "tC/tYield"), side = 3, adj = 0, line = -3)

```



